---
title: "Benchmark of Fleiss' kappa, Cohen's kappa, and the Brennan-Prediger coefficient"
subtitle: "Benchmark for the non-aggregrated functions"
author: "Jonas Moss"
output: html_document
editor: visual
date: 4/25/2023
---

The main benefit of `quadagree` versus `irrCAC` for data on long form is its support for missing data and continuous data, but bootstrapping and transformations can come in handy as well. As it turns out, `quadagree` is sightly faster than `irrCAC` for most practical data sizes. The largest difference is found for Conger's kappa, as the method used by `irrCAC`, which works for any weighting function, must necessarily do much more work for Conger's kappa. For `quadagree`, Fleiss's kappa and Conger's kappa are equally fast.

The following benchmark is being run on $n=50$ ratings and $R=4$ raters.

```{r}
library("quadagree")
x <- dat.zapf2016
irr_conger <- \(x) irrCAC::conger.kappa.raw(x, weights = "quadratic")
irr_fleiss <- \(x) irrCAC::fleiss.kappa.raw(x, weights = "quadratic")
irr_bp <- \(x) irrCAC::bp.coeff.raw(x, weights = "quadratic")
microbenchmark::microbenchmark(
  irr_conger(x),
  congerci(x),
  irr_fleiss(x),
  fleissci(x),
  irr_bp(x),
  bpci(x),
  times = 1000
)
```

Let's try $n=500$.

```{r}
y <- rbind(x, x, x, x, x, x, x, x, x, x)
# 500 ratings
microbenchmark::microbenchmark(
  irr_conger(y),
  congerci(y),
  irr_fleiss(y),
  fleissci(y),
  irr_bp(y),
  bpci(y),
  times = 1000
)
```

For $n=3000$, `quadagree` is roughly $5$ times faster than `irrCAC` for Conger's kappa and the Brennan-Prediger coefficient.

```{r}
z <- rbind(y, y, y, y, y, y, y, y, y, y)
# 5000 ratings
microbenchmark::microbenchmark(
  irr_conger(z),
  congerci(z),
  irr_fleiss(z),
  fleissci(z),
  irr_bp(z),
  bpci(z)
)
```

If we increase the number of categories, the differential becomes very large.

```{r}
w <- cbind(y, y, y, y, y, y, y, y, y, y)
# 500 ratings and 40 categories.
microbenchmark::microbenchmark(
  irr_conger(w),
  congerci(w),
  irr_fleiss(w),
  fleissci(w),
  irr_bp(w),
  bpci(w)
)
```
