---
title: "Using the quadagree package."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{using_quadagree}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(quadagree)
```

Use the `quadagree` package to estimate and do inference on the quadratically weighted Fleiss' kappa and Conger's kappa (the multirater variant of Cohen's kappa). It supports data on two forms: Raw or aggregated. An example of data on "raw" or "wide" form is the following data set with 4 raters and 5 categories from Zapf et al. (2016).

```{r}
knitr::kable(dat.zapf2016)
```

To estimate Fleiss' kappa and Conger's kappa, simply call

```{r}
fleiss(dat.zapf2016)
conger(dat.zapf2016)
```
For inference, use
```{r}
quadagree(dat.zapf2016)
```
and
```{r}
cohenci(dat.zapf2016)
```

It is also possible to use the studentized bootstrap by selecting the option `bootstrap = "TRUE`", but this appears to confer no benefits and we would recommend sticking to the standard methods.

Data on aggregated form looks different, with each row aggregating the number of ratings for each category. The following example is from Fleiss (1971).

```{r}
knitr::kable(dat.fleiss1971)
```

The dataset has categories
```{r}
colnames(dat.fleiss1971)
```
Provided we understand `depression` as being `1`, `personality disorder` as being `2`, and so on, we can calculate and do inference on the quadratically weighted Fleiss kappa (but not Conger's kappa) for data on this form.

```{r}
fleiss_aggr(dat.fleiss1971)
```

Inference is done in a similar way.

```{r}
fleiss_aggr_ci(dat.fleiss1971)
```
